Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-05-21 doc/network.tex
need to commit before I merge

>>>>

We estimate the exponential growth rate $r$ of an epidemic from daily incidence by modeling the cumulative incidence $c(t)$ with a logistic function \citep{ma2014estimating}: 
\begin{equation}
c(t) = \frac{K}{1 + \[(K/c_0) - 1\] e^{-rt}},
\end{equation}
where $K$ is the final size of an epidemic and $c_0$ is the initial number of cases.
Fitting this curve directly to cumulative incidence can lead to overly confident result \citep{king2015avoidable}; instead we fit interval incidence $x(t) = c(t + \Delta t) - c(t)$, where $\Delta t$ is 1 day, to daily incidence, assuming that daily incidence follows a negative binomial distribution. 
This assumption requires us to estimate the dispersion parameter $\theta$ of a negative binomial distribution.
Parameters $r$, $K$, $c_0$, and $\theta$ are estimated simultaneously by maximizing the likelihood.
